Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-20 PAPER.tex
fixed bug in generating figure 11

The single replacement strategy also provides a higher sensitivity estimate as only at most one baseline is repeated in each 
group. In P64, baselines were chosen for groups randomly with replacement. In doing so, $\sim3$$-4$ baselines per group 
were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$55\%$ for $10$ total 
independent samples) which sacrificed some sensitivity.

>>>>

The single replacement strategy also provides a higher sensitivity estimate as only at most one baseline is repeated in each 
group. In P64, baselines were chosen for groups randomly with replacement. In doing so, $\sim3$$-4$ baselines per group 
were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$63\%$ for $10$ total 
independent samples) which sacrificed some sensitivity.
